### 2025-01-16 sections/5-discussion.tex
more offloading to figure captions

As the previous paragraph suggests, the fastest CAKES algorithm varies by dataset.
For example, on Glove-25, Repeated $\rho$-NN exhibits the highest throughput of any CAKES algorithm, despite having the lowest throughput of the three on Sift and Fashion-Mnist.
On Silva, Repeated $\rho$-NN is comparable to the other CAKES algorithms at low multipliers, but becomes the fastest at the higher multipliers.
When we view these results in light of the LFD plots in Figure~\ref{fig:results:lfd-plots}, we realize that Repeated $\rho$-NN appears to be the fastest CAKES algorithm on datasets where a large proportion of the data have a very low LFD, such as Glove-25 and Silva.
This trend is unsurprising, given that Repeated $\rho$-NN relies on a low LFD around the query in order to quickly estimate the correct radius for $k$ hits.
These findings suggest that Repeated $\rho$-NN is the most ``sensitive'' to the manifold structure of the dataset.
Exploring this sensitivity is a potential avenue for future study, as it remains to learn at what LFD Repeated $\rho$-NN transitions away from being the fastest CAKES algorithm, and whether this transition is sharp.

>>>>

As the previous paragraph suggests, the fastest CAKES algorithm varies by dataset.
For example, on Glove-25, Repeated $\rho$-NN exhibits the highest throughput of any CAKES algorithm, despite having the lowest throughput of the three on Sift and Fashion-Mnist.
On Silva, Repeated $\rho$-NN is comparable to the other CAKES algorithms at low multipliers, but becomes the fastest at the higher multipliers.
When we view these results in light of the LFD plots in Figure~\ref{fig:results:lfd-plots}, we realize that Repeated $\rho$-NN appears to be the fastest CAKES algorithm on datasets where a large proportion of the data have a very low LFD, such as Glove-25 and Silva.
This trend is unsurprising, given that Repeated $\rho$-NN relies on a low LFD around the query in order to quickly estimate the correct radius for $k$ hits.
% These findings suggest that Repeated $\rho$-NN is the most ``sensitive'' to the manifold structure of the dataset.
% Exploring this sensitivity is a potential avenue for future study, as it remains to learn at what LFD Repeated $\rho$-NN transitions away from being the fastest CAKES algorithm, and whether this transition is sharp.
